quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-08-31 paper-quollr.Rmd
Adde prediction with other methods
Added the sentence regarding small variance

The remaining variables $X_4$, $X_5$, $X_6$, $X_7$ are all uniform error, with small variance. `scurve_umap` is the UMAP $2\text{-}D$ embedding for `scurve` data with `n_neighbors`$=46$ and `min_dist`$=0.9$. Each data set contains a unique ID column that maps the $7\text{-}D$ point in `scurve` to the corresponding $2\text{-}D$ `scurve_umap`.

@@

>>>>

The remaining variables $X_4$, $X_5$, $X_6$, and $X_7$ are included as low-magnitude noise dimensions, generated from uniform distributions with narrow ranges around zero: $X_4, X_5 \sim U(-0.02, 0.02)$, $X_6 \sim U(-0.1, 0.1)$, and $X_7 \sim U(-0.01, 0.01)$. These small variances ensure that the added dimensions contribute noise without obscuring the main geometric structure. `scurve_umap` is the UMAP $2\text{-}D$ embedding for `scurve` data with `n_neighbors`$=46$ and `min_dist`$=0.9$. Each data set contains a unique ID column that maps the $7\text{-}D$ point in `scurve` to the corresponding $2\text{-}D$ `scurve_umap`.

@@

It is worth noting that while `predict_emb()` provides a general approach that works across methods, some NLDR techniques have their own built-in prediction mechanisms. For example, UMAP (@tomasz2023) supports direct prediction of embeddings for new data once a model is fitted.
